---
title: "Dashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    social: ["twitter", "facebook", "menu"]
    source_code: embed
---

```{r setup, include=FALSE}
library(flexdashboard)
install.packages("plotly")
install.packages("googlesheets4")
install.packages("DT")
install.packages("kableExtra")
install.packages("dplyr")
library(dplyr)
library(kableExtra)
library(DT)
library(googlesheets4)
library(plotly)
library(data.table)
data(diamonds, package = "ggplot2")
diamonds <- data.table(diamonds)
data <- diamonds[sample(.N, 10000)]
data <- data.frame(data)
```



```{r}
gs4_auth(
  cache = "./secrets/.",
  email = "ahmedkhatir22@gmail.com"
)
```

```{r}
Mysheet <- gs4_create(
  "SheetName",
  sheets = list(data)
)
```


Data Visualization
=======================================

Column { data-width=150 }
---------------------------------

### Average of carat

```{r}
valueBox(round(mean(data$carat), 2),
         icon = "fa-chart-area",
         color = "forestgreen")
```


### Average of price

```{r}
valueBox(round(mean(data$price), 2), 
         icon = "fa-credit-card",
         color = "purple")
```

### Average of depth

```{r}
valueBox(round(mean(data$depth), 2), 
         icon = "fa-signal",
         color = "#e5383b")
```

###  Diamonds price index

```{r}
gauge(round(data$price,
            digits = 2),
      min = 0,
      max = 18823,
      gaugeSectors(success = c(0, 15000),
                   warning = c(15000,18500),
                   danger = c(18500,18823),
                   colors = c("green", "yellow", "red")))
```

### Average length

```{r}
valueBox(round(mean(data$x), 2), 
         icon = "fa-signal",
         color = "#1f77b4")
```


Column { data-width=425 }
---------------------------------

### Bar chart of the quality of the cut by clarity

```{r}
plot_ly(data, x = ~cut, color = ~clarity, colors = "Accent")
```

### Scatter plot of carat vs price

```{r, warning=FALSE, message=FALSE}
plot_ly(data, x = ~carat, y = ~price, color = ~cut,
        size = ~carat, text = ~paste("Color: ", color))
```

Column { data-width=425 }
---------------------------------

### Pie plot for cut, clarity and color

```{r, warning=FALSE, message=FALSE}
fig <- plot_ly()
fig <- fig %>% add_pie(data = count(data, cut), labels = ~cut, values = ~n,
                       name = "Cut", domain = list(x = c(0, 0.4), y = c(0.4, 1)))
fig <- fig %>% add_pie(data = count(data, color), labels = ~color, values = ~n,
                       name = "Color", domain = list(x = c(0.6, 1), y = c(0.4, 1)))
fig <- fig %>% add_pie(data = count(data, clarity), labels = ~clarity, values = ~n,
                       name = "Clarity", domain = list(x = c(0.25, 0.75), y = c(0, 0.6)))
fig <- fig %>% layout(title = "Pie Charts with Subplots", showlegend = F,
                      xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
                      yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))

fig
#plot_ly(data, x = ~cut, y = ~clarity)
```


### Donut charts of color

```{r}
df <- data %>% group_by(clarity)
df <- df %>% summarize(count = n())
fig <- df %>% plot_ly(labels = ~clarity, values = ~count)
fig <- fig %>% add_pie(hole = 0.6)
fig <- fig %>% layout(title = "Donut charts of color",  showlegend = F,
                      xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
                      yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))

fig
#plot_ly(data, x = ~color, color = I("red"), stroke = I("black"), span = I(2))
```



Summary {data-orientation=columns}
===============================================

columns
-----------------------------------------------

### Min of Diamod Price

```{r}
valueBox(min(data$price),
         icon = "fa-bolt")
```


### Max of Diamond Price

```{r}
valueBox(max(data$price),
         icon = "fa-bullhorn")
```

### Average Price of Diamonds

```{r}
valueBox(round(mean(data$price),
         digits = 2),
         icon = "fa-area-chart")
```


### Volatility of Diamnod Price

```{r}
valueBox(round(sqrt(var(data$price)),
         digits = 2),
         icon = "fa-chart-line")
```


Rows 
-----------------------------------------

Report

* This is a report on `r min(data$price)` diamond price.

* This is a report on `r max(data$price)` diamond price.

* The average of diamonds was `r mean(data$price)`.

* The variance of the diamonds was `r sqrt(var(data$price))`.

This report was generated on `r format(Sys.Date(), format = "%B %d, %Y" )`.


Dataset description
=======================================


### Variable description

Here’s what we know about the diamonds dataset:

* This dataset contains information about 53,940 round-cut diamonds. How do we know? Each row of data represents a different diamond and there are 53,940 rows of data (see help page, ?diamonds).

* There are 10 variables measuring various pieces of information about the diamonds. Notice that these variable names are in lowercase. We can take a quick view of the variable names using.

```{r}
Variable <- c("Price", "Carat", "Cut", "Color", "Clarity",
              "X", "Y", "Z", "Depth", "Table")
Description <- c("price in US dollars",
                 "weight of the diamond",
                 "quality of the cut",
                 "diamond color",
                 "measurement of how clear the diamond is",
                 "length in mm", "width in mm","depth in mm",
                 "total depth percentage",
                 "width of top of diamond relative to widest point")
Values <- c("$326-$18,823", "0.2-5.01",
            "Fair, Good, Very Good, Premium, Ideal",
            "J (worst) to D (best)",
            "I1 (worst), SI2, SI1, VS2, VS1, VVS2, VVS1, IF (best)",
            "0-10.74", "0-58.9", "0-31.8", "43-79",
            "43-95")
tab <- data.frame(Variable, Description, Values)
knitr::kable(tab,"pipe", align = c("l","c", "c"), caption = "Daimond Dataset")
```


There are 3 variables with an ordered factor structure: cut, color, & clarity. An ordered factor arranges the categorical values in a low-to-high rank order. For example, there are 5 categories of diamond cuts with “Fair” being the lowest grade of cut to ideal being the highest grade.

* There are 6 variables that are of numeric structure: carat, depth, table, x, y, z

* There is 1 variable that has an integer structure: price

Remember that R will always have documentation (in the help page; ?diamonds) for built-in datasets. The descriptiveness for the documentation will vary, depending on the package author.

Data Table
============================================


```{r}
# put CSV, XLS, and PDF in a collection
datatable(
  data,
  extensions = 'Buttons', options = list(pageLength = 25,
    dom = 'Bfrtip',
    buttons = 
      list('copy', 'print', list(
        extend = 'collection',
        buttons = c('csv', 'excel'),
        text = 'Download'
      ))
    
  )
)
```
