---
title: "Dashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
    social: ["twitter", "facebook", "menu"]
    source_code: embed
---

```{r setup, include=FALSE}
library(flexdashboard)
install.packages("plotly")
install.packages("googlesheets4")
install.packages("DT")
library(DT)
library(googlesheets4)
library(plotly)
library(data.table)
data(diamonds, package = "ggplot2")
diamonds <- data.table(diamonds)
data <- diamonds[sample(.N, 10000)]
data <- data.frame(data)
```




```{r}
gs4_auth(
  cache = "./secrets",
  email = "ahmedkhatir22@gmail.com"
)
```

```{r}
Mysheet <- gs4_create(
  "SheetName",
  sheets = list(data)
)
```





Data Visualization
=======================================

Rows
---------------------------------

### Average of carat

```{r}
valueBox(round(mean(data$carat), 3),
         icon = "fa-chart-area")
```


### Average of price

```{r}
valueBox(round(mean(data$price), 3), 
         icon = "fa-credit-card")
```

### Average of depth

```{r}
valueBox(round(mean(data$depth), 3), 
         icon = "fa-signal")
```

###  Diamonds price index

```{r}
gauge(round(mean(data$price),
            digits = 2),
            min = 0,
            max = max(data$price),
            gaugeSectors(success = c(0,min(data$price)),
                         warning = c(min(data$price),mean(data$price)),
                         danger = c(mean(data$price),max(data$price)),
                         colors = c("green", "yellow", "red")))
```



column {data-width=350}
---------------------------------

### Bar chart of the quality of the cut by clarity

```{r}
plot_ly(data, x = ~cut, color = ~clarity, colors = "Accent")
```

### Scatter plot of carat vs price

```{r}
p4 <- plot_ly(data, x = ~price) %>%
  add_markers(y = ~carat,
              text = ~paste('Carat: ', carat),
              showlegend = F) %>%
  add_lines(y = ~fitted(loess(carat ~price)),
            name = 'Loes Smoother',
            color = I("#FFC125"),
            showlegend =T,
            line = list(width = 5)) %>%
  layout(xaxis = list(title = "Price"),
         yaxis = list(title = "Carat"))
p4
```

columns {data-width=350}
---------------------------------

### Heatmap of cut vs clarity

```{r}
plot_ly(data, x = ~cut, y = ~clarity)
```


### Scatter plot of cut

```{r}
plot_ly(data, x = ~cut, color = I("red"), stroke = I("black"), span = I(2))
```


Data Table
============================================


```{r}
# put CSV, XLS, and PDF in a collection
datatable(
  data,
  extensions = 'Buttons', options = list(pageLength = 25,
    dom = 'Bfrtip',
    buttons = 
      list('copy', 'print', list(
        extend = 'collection',
        buttons = c('csv', 'excel'),
        text = 'Download'
      ))
    
  )
)
```


Summary {data-orientation=columns}
===============================================

columns
-----------------------------------------------

### Min of Diamod Price

```{r}
valueBox(min(data$price),
         icon = "fa-bolt")
```


### Max of Diamond Price

```{r}
valueBox(max(data$price),
         icon = "fa-bullhorn")
```

### Average Price of Diamonds

```{r}
valueBox(round(mean(data$price),
         digits = 2),
         icon = "fa-area-chart")
```


### Volatility of Diamnod Price

```{r}
valueBox(round(sqrt(var(data$price)),
         digits = 2),
         icon = "fa-chart-line")
```


Rows 
-----------------------------------------

Report

* This is a report on `r min(data$price)` diamond price.

* This is a report on `r max(data$price)` diamond price.

* The average of diamonds was `r mean(data$price)`.

* The variance of the diamonds was `r sqrt(var(data$price))`.

This report was generated on `r format(Sys.Date(), format = "%B %d, %Y" )`.
